%-------------------------
% resume in Latex
% Author : Avnish Sachar
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\rItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\rItemDesc}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}
\newcommand{\rItemDescp}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-6pt}}
  }
}

\newcommand{\rSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\rSubItem}[2]{\rItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\rSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\rSubHeadingListEnd}{\end{itemize}}
\newcommand{\rItemListStart}{\begin{itemize}}
\newcommand{\rItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CONTENT  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://avnishsachar.gitlab.io/}{\Large AVNISH SACHAR}} & \faEnvelopeO \href{mailto:avnishsachar1@gmail.com}{ avnishsachar1@gmail.com}\\
  \faHome \href{http://avnishsachar.github.io/}{ avnishsachar.github.io}  & \faGitlab \href{https://gitlab.com/avnishsachar}{ avnishsachar}\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \rSubHeadingListStart
    \rSubheading
      {Manipal Institute of Technology}{Manipal, India}
      {Bachelor of Technology in Mechatronics Engineering;  GPA: 3.43 (8.17/10)}{August 2015 -- Present}
    \rSubheading
      {Delhi Public School Gurgaon}{Gurgaon, India}
      {All India Senior School Certificate Examination, CBSE;  Grade: 91.8\%}{August 2013 -- July 2015}
     \rSubheading
      {Delhi Public School Gurgaon}{Gurgaon, India}
     {All India Secondary School Examination, CBSE;  GPA: 10/10}{August 2011 -- July 2013}
      
  \rSubHeadingListEnd


%--------SKILLS------------
\section{Skills}

\rSubHeadingListStart
    \rSubItem{Programming/Scripting Languages}
      {Python, C++, MATLAB, C}
    \rSubItem{Frameworks and Tools}
      {Robot Operating System (ROS), GazeboSim, CATIA, Solidworks, AutoCAD, Git, \LaTeX}
    \rSubItem{Languages}
      {English, Hindi, French (intermediate), German (beginner)}
\rSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \rSubHeadingListStart

    \rSubheading
      {Biorobotics Laboratory, \'Ecole Polytechnique F\'ed\'erale de Lausanne(EPFL)}{Lausanne, Switzerland}
      {Research Intern}{June 2018 - July 2018}
      \rItemListStart
        \rItemDesc{}
          {Developed a neuromechanical framework using ROS to study amphibian locomotion under Prof. Auke Jan Ijspeert.}
        \rItemDesc{}
          {Simulated and analyzed neuromechanical controllers for different tetrapod morphologies.}
        \rItemDesc{}
          {Research supported by the Human Frontier Science Program (HFSP) for the Robotics-Inspired Biology project}
      \rItemListEnd

    \rSubheading
      {Mechatronics Laboratory, IIT Delhi}{New Delhi, India}
      {Intern}{May 2017 - July 2017}
      \rItemListStart
        \rItemDesc{}
          {Developed a wearable energy expenditure device under Dr. Sudipto Mukherjee.}
        \rItemDesc{}
          {Studied capnographic and calorie expenditure data for humans.}
      \rItemListEnd

    \rSubheading
      {Formula Manipal}{Manipal, India}
      {Electronics Engineer}{March 2016 -- Feburary 2017}
      \rItemListStart
        \rItemDesc{}
        {Placed 9\textsuperscript{th} overall in Formula Bharat 2017.}
        \rItemDesc{}
        {Designed and developed an open-wheel Formula SAE car.}
        \rItemDesc{}
          {Developed a data acquisition (DAq) system.}
        \rItemDesc{}
          {Devised a closed lop shifting and clutching system for the transmission.}
        \rItemDesc{}
        {Developed an automated Drag Reduction System as a part of the aerodynamic package.}

      \rItemListEnd
  \rSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \rSubHeadingListStart
    \rItemDescp{}
      {Obstacle detection and Path planning for an autonomous robot using computer vision and fuzzy logic.}
   \rItemDescp{}
      {Modelling and simulating a salamander like robot in ROS and Gazebo.}
       \rItemDescp{}
      {Linear-quadratic generator (LQR) based control of a 3-link Linear Inverted Pendulum on a cart in ROS.}

    \rItemDescp{}
      {Developing a neuromechanical controller for a humanoid using Central Pattern Generators.}
    \rItemDescp{}
      {Modelling and simulation of MTAB-Aristo robotic arm in MATLAB.}
    \rItemDescp{}
      {Speech Enhancement using Extended Kalman Filter in MATLAB.}
  \rSubHeadingListEnd
%-----------Positions-----------------
\section{Positions of Responsibility}
  \rSubHeadingListStart
    \rSubheading
      {Teaching Assistant- Robot Dynamics and Control (MTE 4007)}{Manipal, India}
      {Manipal Institute of Technology}{August 2018 - Present}
      \rItemListStart
        \rItemDesc{}
          {Teaching ROS to a class of 42 undergraduates.}
        \rItemDesc{}
          {Prepared lessons and assignments, evaluating final projects.}
      \rItemListEnd
    \rSubheading
      {Co-founder-- Biorobotics Group, Manipal}{Manipal, India}
      {Manipal Institute of Technology}{September 2018 - Present}
      \rItemListStart
        \rItemDesc{}
          {Conducting research on central pattern generators based neuromechanical models for animal locomotion.}
        \rItemDesc{}
            {Managing the recruitment and operations for the group.}
      \rItemListEnd
    \rSubheading
      {Vice-Head-- Student Council}{Gurgaon, India}
      {Delhi Public School Gurgaon}{July 2013 - July 2014}
      \rItemListStart
        \rItemDesc{}
          {Planned and organized various events.}
        \rItemDesc{}
          {Supervised a team of 40 council members.}
      \rItemListEnd
  \rSubHeadingListEnd
%-----------Online Courses-----------------
\section{Online Courses}
  \rSubHeadingListStart
    \rItemDescp{}
      {Robotics: Computational Motion Planning by University of Pennsylvania on Coursera. Certificate earned on Wednesday, October 3, 2018. Grade Achieved: 100.0\%.}
  \rSubHeadingListEnd
%-----------EXTRA CURRICULAR-----------------
\section{Extra Curricular Activities}
  \rSubHeadingListStart
    \rItemDescp{}
      {Played for the Gurgaon District team in the Haryana State Level Basketball Tournament (Under-17).}
    \rItemDescp{}
      {Committee Member, International Association for the Exchange of Students for Technical Experience (IAESTE), Manipal.}
  \rSubHeadingListEnd
\end{document}